Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-07 Response/response-3.tex

\begin{enumerate}
\cmnt{1} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.

\resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not required as a variable. However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).
	\begin{enumerate}
		\item (6), (16), (20) and (21) does not depend upon the variable \me{t_k}
		\item (26) and (28) depend on the variable \me{t_k} and it is defined as an optimization variable.
	\end{enumerate}	
	}

\cmnt{2} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5). This is not obvious. An easy case to check this statement is that assuming the system has two BS and each BS serves one user. When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality. Rigorous proof is needed if authors stick to this statement.

\resp \review{We thank the reviewer for the insightful comment. We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) together provides an under-estimator for the SINR expression in (2). This information is highlighted in the third paragraph in Section III-B.}

\review{For the constraints (16b) and (16c) to be tight, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget. On the other hand, to make the constraints active in all cases, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
\begin{equation}
\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right )
\end{equation}
where \me{\varphi \approx 0}. Note that the modified objective will relax the power constraint by making the constraints (16b) and (16c) tight in the final solution. Note that the tightness discussion is valid only for the active spatial streams, \textit{i.e}, \me{\mvec{m}{l,k,n} \neq \mbf{0}^\tran}.
}
\begin{comment}
	\begin{enumerate}
		\item We thank the reviewer for the insightful comment. We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under-estimator for the SINR expression in (2) on the third paragraph in Section III-B.
		\item The under-estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A. It is not tight when the objective is zero even for a single BS. For this, we can regularize the objective with the total transmitted power as
		\begin{equation}
		\|\tilde{\mbf{v}}\|_q + \varphi \, \|\mbf{m}\|^2
		\end{equation} 
		where \me{\mbf{m}} is the stacked vector of all transmit precoders and \me{\varphi} is a constant chosen closer to zero such that it has no effect on the optimal solution. When the original objective is zero, \textit{i.e}, \me{\|\tilde{\mbf{v}}\| = 0}, the the problem becomes the min power design. Therefore, when the backlogged packets can be transmitted with the given power constraint, the regularized objective will find a minimum power precoders to empty the backlogged packets. It makes the objective tight at the optimal point.
		\item Note that the regularized objective makes the inequalities (16b) and (16c) tight at the optimal solution by making the power constraint in (16d) loose. It is discussed in Appendix A provided on the supplementary document.
	\end{enumerate}
	 }
\end{comment}

### 2015-04-07 Report/convergence_centralized.tex
adhi-alarm

\subsection{Bounded Objective Function and Compact Feasible Set}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.

>>>>

\subsection{Bounded Objective Function and Compact Feasible Set}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.

### 2015-04-07 Report/wsrm_formulation.tex
adhi
adhi-alarm

\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \ac{SCA} \cite{marks1978technical}. The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system. The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint. Using additional variables, we relax the expression in \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
\iftoggle{single_column}{
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \label{eqn-6.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-6}
	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
\end{IEEEeqnarray}
}
\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}. Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}. Using the relaxation for the \ac{SINR} constraint, \eqref{eqn-6} provides an equivalent formulation for the problem in \eqref{eqn-3}.	Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore, it also belongs to the class of NP-hard problem.}

>>>>

\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \ac{SCA} \cite{marks1978technical}. The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system. The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint. Using additional variables, we relax the expression in \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
\iftoggle{single_column}{
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \label{eqn-6.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-6}
	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
\end{IEEEeqnarray}
}
\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}. Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}. Therefore, the formulation in \eqref{eqn-6} is an equivalent approximation for the problem presented in \eqref{eqn-3}. Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore it belongs to the class of NP-hard problems.}
